Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-14 sections/correlated-sicm-and-fm.tex
reworked Astrid'S paragraph

Although recording SICM and FM data independently on different samples under
the same conditions can support conclusions that could not be drawn from data
from a single technique alone \cite{Gesper2017,Lee2013,Lyon2009}, we will
focus on applications were SICM and FM data has been recorded from the same
sample. Furthermore, we focus on far-field FM techniques and do not review the
combination of SICM with nearfield optical microscopy  
\cite{Korchev2000,Shevchuk2001,Rothery2003,Bruckbauer2002}. We also do not review
studies, that use the nanopipette for targeted deposition 
\cite{Ying2002,Bruckbauer2007,Bruckbauer2010,Hennig2015} or for injection 
\cite{Hennig2015a} of fluorescent/fluorescently-labeled molecules. As well, as studies, 
where the nanopipette was used for manipulation \cite{Fuentes2012,Wang2020} or as a 
fluorescence-based nanosensor \cite{Piper2006}.

>>>>

Although recording SICM and FM data independently on different samples under
the same conditions can support conclusions that could not be drawn from data
from a single technique alone \cite{Gesper2017,Lee2013,Lyon2009}, we will
focus on applications were SICM and FM data has been recorded from the same
sample. Furthermore, we focus on far-field FM techniques and do not review the
combination of SICM with nearfield optical microscopy  
\cite{Korchev2000,Shevchuk2001,Rothery2003,Bruckbauer2002} or studies where
the SICM pipette is used for targeted deposition 
\cite{Ying2002,Bruckbauer2007,Bruckbauer2010,Hennig2015} or for injection 
\cite{Hennig2015a} of molecules, as a nano-sensor \cite{Piper2006} or for manipulating the sample
\cite{Fuentes2012,Wang2020}.
